Pillar 2 - Topic Modeling

### 2019-03-01 Pillar_2_-_Topic_Modeling.Rmd
old version

```{r LDA fit, cache = TRUE}
n_topics <- 5
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

@@

save(list = list_nam,
     file = "LDA.RDATA")
```

## Visualization
### Functions
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(results){

>>>>

##OLD Version:
```{r LDA fit, cache = TRUE}
n_topics <- 5
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

@@

save(list = list_nam,
     file = "LDA.RDATA")
```
#end of old version
## Visualization
### Functions
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(results){
